Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-04-21 manuscript/manuscript.tex
ms updates

In analyzing both the empirical datasets included in our study and our
simulation results, we noticed the temporal covariances and $G(t)$ statistics
are sensitive to how fixations are handled. Through simulations and comparing
the results of analyzing our empirical datasets both ways, we have found
tradeoffs to both approaches, but overall not removing fixed sites is a more
conservative, safer approach, and is what we use throughout our paper.

Temporal covariances (and related statistics like convergence correlations,
$G(t)$, etc.) are calculated on allele frequency changes, $\Delta p_t$; when an
allele is fixed or lost, the allele frequency changes are zero thereafter
$\Delta p_t = 0$. When temporal covariance is calculated by averaging over the
loci in a region or across the genome, fixed sites zero out the terms in the
sum of the right hand side of temporal covariance, $\cov(\Delta p_t, \Delta
p_s) = \E(\Delta p_t \Delta p_s) - \E(\Delta p_t) \E(\Delta p_s)$ and can
shrink the second terms towards zero.

@@

>>>>

In analyzing both the empirical datasets included in our study and our
simulation results, we noticed the temporal covariances and $G(t)$ statistics
are sensitive to how fixations are handled. Through simulations and comparing
the results of analyzing our empirical datasets both ways, we have found
trade-offs to both approaches, but overall find that not removing fixed sites
is a more conservative, safer approach, and is what we use throughout our
paper.

Temporal covariances (and related statistics like convergence correlations,
$G(t)$, etc.) are calculated on allele frequency changes, $\Delta p_t$; when an
allele is fixed or lost, the allele frequency changes are zero thereafter
$\Delta p_t = 0$. When temporal covariance is calculated by averaging over the
loci in a region or across the genome, fixed sites zero out the terms in the
sum of the right hand side of temporal covariance, $\cov(\Delta p_t, \Delta
p_s) = \E(\Delta p_t \Delta p_s) - \E(\Delta p_t) \E(\Delta p_s)$ and can
shrink the second terms towards zero. From simulations, we have found that
including neutral sites into the temporal covariance calculation that are lost
or fix will tend to shrink the covariance towards zero, and in some cases
create a spurious negative temporal covariance. We observed this when
conducting the background selection simulations of Supplementary Materials
Section XXX, and have included an alternative version of this figure that
includes $G(t)$ trajectories calculated by including fixed neutral sites
(Supplementary Figure \ref{suppfig:supp-bgs-g-fix}).

In cases where neutral
sites are rapidly lost or fixed, this can result in negative covariances.

@@

  \label{suppfig:supp-bgs-g-fix}
\end{figure}
